#0 Common script
#1 PAM data (graph)
    #1.1 Graph FvFm Figure2C
    #1.2 Stats
       #1.2.1 FvFm (over all experiment)
#2 GROWTH data (graph and stats)
    #2.1 Percentage change in Area
      #2.1.1 Graph
      #2.1.2 Stats  
         #2.1.2.1 Single Lm and use the contrast matrix to test the differences
    #2.2 TO growth 
       #2.2.1 Graph
       #2.2.2 Stats  
          #2.2.2.1 Single Lm and use the contrast matrix to test the differences. KEEPER
#3 Survivorship  (graph and stats)   
    #3.1.1 Percentage survivorship graph
    #3.2 Percentage survivorship stats
#4 Respiration
    #4.1 Bar graph
    #4.2 Stats 
#5 Cell densities
    #5.1 Bar graph Cell densities per mm2
        #5.1.1 Linear model T00
        #5.1.2 Linear model T33
    #5.2 Bar graph Propor Change in Cell densities per mm2
        #5.2.1 Linear model
    #5.3 Propor Change in Cell densities per mm2 per time point within culture and temp change 
        #5.3.1 Bar graph  
        #5.3.2 Linear model
        








# 0 Common script  
```{r}
NanoSIMSAll<-read.csv("NanoSIMS.csv",header=T,strip.white=TRUE)
head(NanoSIMSAll)


NanoSIMSAll$Temperature<-as.factor(NanoSIMSAll$Temperature)
NanoSIMSAll$Disk<-as.factor(NanoSIMSAll$Disk)
NanoSIMSAll$JuvID<-as.factor(NanoSIMSAll$JuvID)
NanoSIMSAll$DayAsFactor<-NanoSIMSAll$Day #add a column with Day as factor
NanoSIMSAll$DayAsFactor<-as.factor(NanoSIMSAll$DayAsFactor)


head(NanoSIMSAll)
```

Filter data to keep just day 00 and remove clusters

```{r}
library(dplyr)
T00NanoSIMS=filter(NanoSIMSAll,Day==00&Dead=="no")%>% droplevels()
str(T00NanoSIMS)
head(T00NanoSIMS)
tail(T00NanoSIMS)
```

Filter data to keep just day 33 and remove clusters
```{r}
library(dplyr)
T33NanoSIMS=filter(NanoSIMSAll,Day==33&Dead=="no")%>% droplevels() 
str(T33NanoSIMS)
str(T33NanoSIMS$Day) # to double check that we only keep day 33
str(T33NanoSIMS$Dead) #to double check that we only keep the live ones and no clusters or dead ones
head(T33NanoSIMS)
tail(T33NanoSIMS)
```

Filter data to keep just day 0 and 33 and remove clusters
```{r}
library(dplyr)
T0033NanoSIMS=filter(NanoSIMSAll,Day%in% c('0','33') &Dead=="no")%>% droplevels() 
str(T0033NanoSIMS)
str(T0033NanoSIMS$Day) # to double check that we only keep day 33 and 0
str(T0033NanoSIMS$Dead) #to double check that we only keep the live ones and no clusters or dead ones
head(T0033NanoSIMS)
tail(T0033NanoSIMS)
```


# Summary function
```{r}
summarySE <- function(data=NULL, measurevar, groupvars=NULL, na.rm=FALSE,
                      conf.interval=.95, .drop=TRUE) {
  require(plyr)
  
  
  # New version of length which can handle NA's: if na.rm==T, don't count them
  length2 <- function (x, na.rm=FALSE) {
    if (na.rm) sum(!is.na(x))
    else       length(x)
  }
  
  # This does the summary. For each group's data frame, return a vector with
  # N, mean, and sd
  datac <- ddply(data, groupvars, .drop=.drop,
                 .fun = function(xx, col) {
                   c(N    = length2(xx[[col]], na.rm=na.rm),
                     mean = mean   (xx[[col]], na.rm=na.rm),
                     sd   = sd     (xx[[col]], na.rm=na.rm)
                   )
                 },
                 measurevar
  )
  
  # Rename the "mean" column    
  datac <- rename(datac, c("mean" = measurevar))
  
  datac$se <- datac$sd / sqrt(datac$N)  # Calculate standard error of the mean
  
  # Confidence interval multiplier for standard error
  # Calculate t-statistic for confidence interval: 
  # e.g., if conf.interval is .95, use .975 (above/below), and use df=N-1
  ciMult <- qt(conf.interval/2 + .5, datac$N-1)
  datac$ci <- datac$se * ciMult
  
  return(datac)
}
```



# 1 PAM data (Graph)

Filter data to remove those values with F<0.1
```{r}
library(dplyr)
PAMNanoSIMS=filter(NanoSIMSAll,F>0.1 & F<0.3)
head(PAMNanoSIMS)
```

Filter data to remove those values from T0 for FvFm percentage change
```{r}
library(dplyr)
PAMNanoSIMSNoT0=filter(PAMNanoSIMS,Day>0)%>% droplevels() 
str(PAMNanoSIMSNoT0)
head(PAMNanoSIMSNoT0)
```

Create and Save Summary
```{r}
summaryfvfm<-summarySE(PAMNanoSIMS, measurevar="FvFm", groupvars=c("Day","Culture","Temperature","Treatment"),na.rm=TRUE,conf.interval=0.95)
summaryfvfm

summaryfvfmPerTemperature<-summarySE(PAMNanoSIMS, measurevar="FvFm", groupvars=c("Culture","Temperature","Treatment"),na.rm=TRUE,conf.interval=0.95)
summaryfvfmPerTemperature

summaryfvfmchange<-summarySE(PAMNanoSIMS, measurevar="FvFmPercentageChange", groupvars=c("Day","Culture","Temperature","Treatment"),na.rm=TRUE,conf.interval=0.95)
summaryfvfmchange

```

#1.1 Graph FvFm Figure2C
```{r}
library(ggplot2)
summaryfvfm$Culture=factor(summaryfvfm$Culture,levels=c("WT10","SS01","SS08"), labels = c("WT10","SS1","SS8")) #change the order of the factors so that they show in the graph in the desired order

Figure2C_NanoSIMSFvFmGraph=ggplot(summaryfvfm, aes(y=FvFm, x=Day, color=Culture))+
            facet_grid(Temperature~.)+
            geom_line(aes(colour=Culture))+
            scale_colour_manual(values=c("#A4D3CC","#CE9884","#871719"))+
            geom_ribbon(aes(ymin=FvFm-se, ymax=FvFm+se),position=position_dodge(0.01),fill = "grey90",alpha = 0.3) +
            geom_point(size=1)+
            scale_y_continuous (expression("Fv/Fm"))+ 
            scale_x_continuous(breaks=0:33*3)+
            theme_bw()
Figure2C_NanoSIMSFvFmGraph


```


#1.2 Stats
   #1.2.1 FvFm (over all experiment)
```{r}
library(nlme)
library(lme4)
head(PAMNanoSIMS)
str(PAMNanoSIMS$Disk)
NanoSIMSPAM.lme1<-lme(FvFm~Treatment,random = ~1|Disk, data=PAMNanoSIMS, method="REML")
NanoSIMSPAM.lme2<-lme(FvFm~Treatment*Day,random = ~1|Disk, data=PAMNanoSIMS, method="REML")
NanoSIMSPAM.lme3<-lme(FvFm~Treatment*Day,random = ~1|Disk/JuvID, data=PAMNanoSIMS, method="REML")
NanoSIMSPAM.lme4<-lme(FvFm~Treatment*Day,random = ~1|Disk/JuvID, correlation=corCompSymm(form=~Day|Disk/JuvID),data=PAMNanoSIMS, method="REML")
NanoSIMSPAM.lme5<-lme(FvFm~Temperature*Culture*Day,random = ~1|Disk, data=PAMNanoSIMS, method="REML")
NanoSIMSPAM.lme6<-lme(FvFm~Temperature*Culture*Day,random = ~1|Disk/JuvID, data=PAMNanoSIMS, method="REML")
NanoSIMSPAM.lme7<-lme(FvFm~Temperature*Culture*Day,random = ~1|Disk/JuvID, correlation=corCompSymm(form=~Day|Disk/JuvID), data=PAMNanoSIMS, method="REML")
```

model selection using AIC
```{r}
library(MuMIn)
AIC(NanoSIMSPAM.lme1) #-8821.237
AIC(NanoSIMSPAM.lme2) #-9028.797
AIC(NanoSIMSPAM.lme3) #-10188.3  
AIC(NanoSIMSPAM.lme4) #-10186.3
AIC(NanoSIMSPAM.lme5) #-9028.797
AIC(NanoSIMSPAM.lme6) #-10188.3  Therefore this is the best model
AIC(NanoSIMSPAM.lme7) #-10186.3

```

model validation
```{r}
plot(NanoSIMSPAM.lme6) #no wedge shape
qqnorm(resid(NanoSIMSPAM.lme6))+qqline(resid(NanoSIMSPAM.lme6)) # the second graph
```
#contrast matrix

```{r}
ModelForContrast<-lm(FvFm~Temperature*Culture*Day, data=PAMNanoSIMS)
#contrast matrix
library(contrast)

   a1=contrast(ModelForContrast, 
           a=list(Temperature='27',Culture='SS01',Day=unique(PAMNanoSIMS$Day)), 
           b=list(Temperature='27',Culture='SS08',Day=unique(PAMNanoSIMS$Day))
   ) 

   a1Mean=t(as.matrix(colMeans(a1$X))) #calculate the mean 

   b1=contrast(ModelForContrast, 
           a=list(Temperature='27',Culture='SS01',Day=unique(PAMNanoSIMS$Day)), 
           b=list(Temperature='27',Culture='WT10',Day=unique(PAMNanoSIMS$Day))
   ) 

   b1Mean=t(as.matrix(colMeans(b1$X))) #calculate the mean 

   c1=contrast(ModelForContrast, 
           a=list(Temperature='27',Culture='SS08',Day=unique(PAMNanoSIMS$Day)), 
           b=list(Temperature='27',Culture='WT10',Day=unique(PAMNanoSIMS$Day))
   ) 

   c1Mean=t(as.matrix(colMeans(c1$X))) #calculate the mean 

   
   d1=contrast(ModelForContrast, 
           a=list(Temperature='27',Culture='SS01',Day=unique(PAMNanoSIMS$Day)), 
           b=list(Temperature='31',Culture='SS01',Day=unique(PAMNanoSIMS$Day))
   ) 

   d1Mean=t(as.matrix(colMeans(d1$X))) #calculate the mean 

   e1=contrast(ModelForContrast, 
           a=list(Temperature='27',Culture='SS08',Day=unique(PAMNanoSIMS$Day)), 
           b=list(Temperature='31',Culture='SS08',Day=unique(PAMNanoSIMS$Day))
   ) 

   e1Mean=t(as.matrix(colMeans(e1$X))) #calculate the mean 

   f1=contrast(ModelForContrast, 
           a=list(Temperature='27',Culture='WT10',Day=unique(PAMNanoSIMS$Day)), 
           b=list(Temperature='31',Culture='WT10',Day=unique(PAMNanoSIMS$Day))
   ) 

   f1Mean=t(as.matrix(colMeans(f1$X))) #calculate the mean 

   
   g1=contrast(ModelForContrast, 
           a=list(Temperature='31',Culture='SS01',Day=unique(PAMNanoSIMS$Day)), 
           b=list(Temperature='31',Culture='SS08',Day=unique(PAMNanoSIMS$Day))
   ) 

   g1Mean=t(as.matrix(colMeans(g1$X))) #calculate the mean 

   h1=contrast(ModelForContrast, 
           a=list(Temperature='31',Culture='SS01',Day=unique(PAMNanoSIMS$Day)), 
           b=list(Temperature='31',Culture='WT10',Day=unique(PAMNanoSIMS$Day))
   ) 

   h1Mean=t(as.matrix(colMeans(h1$X))) #calculate the mean 

   i1=contrast(ModelForContrast, 
           a=list(Temperature='31',Culture='SS08',Day=unique(PAMNanoSIMS$Day)), 
           b=list(Temperature='31',Culture='WT10',Day=unique(PAMNanoSIMS$Day))
   ) 

   i1Mean=t(as.matrix(colMeans(i1$X))) #calculate the mean 

   
   
   FvFmMatrixTry1=rbind(a1Mean,b1Mean,c1Mean,d1Mean,e1Mean,f1Mean,g1Mean,h1Mean,i1Mean) #create the matrix
   FvFmMatrixTry1

#run the contrast matrix in the model
library(multcomp)
t <- glht(NanoSIMSPAM.lme6, linfct = FvFmMatrixTry1)
t
summary(t) 
```



#2 GROWTH data (graph and stats)
  #2.1 Percentage change in Area
        2.1.1 Graphs
  
Look at the data from day 33
```{r}
str(T33NanoSIMS)
str(T33NanoSIMS$Day) # to double check that we only keep day 33
str(T33NanoSIMS$Dead) #to double check that we only keep the live ones and no clusters or dead ones
head(T33NanoSIMS)
tail(T33NanoSIMS)
```



Create and Save Summary
```{r}
summaryPropGrowthArea<-summarySE(T33NanoSIMS, measurevar="Area_mm2_PercentageChange", groupvars=c("Culture","Temperature","Treatment"),na.rm=TRUE,conf.interval=0.95)
summaryPropGrowthArea


write.csv(summaryPropGrowthArea,"summaryPropGrowthArea.csv")
summaryPropGrowthArea

```



#bar graph 
```{r}
library(ggplot2)
summaryPropGrowthArea$Culture=factor(summaryPropGrowthArea$Culture,levels=c("WT10","SS01","SS08"), labels = c("WT10","SS1","SS8"))#change the order of the factors so that they show in the graph in the desired order

Figure4B_PropGrowthArea=ggplot(summaryPropGrowthArea, aes(x=Temperature, y=Area_mm2_PercentageChange,fill=Culture))+
          scale_fill_manual(values=c("#A4D3CC","#CE9884","#871719"))+
          geom_bar(stat="identity", position=position_dodge(.9))+
          geom_errorbar(aes(ymin=Area_mm2_PercentageChange-se, ymax=Area_mm2_PercentageChange+se),position=position_dodge(.9),width=0.3)+
          scale_y_continuous (expression("T"[33]~" Percentage Change Area (%)"))+
          scale_x_discrete('Temperature')+
          theme_bw()
Figure4B_PropGrowthArea
```


   #2.1.2 Stats

      #2.1.2.1 Single Lm and use the contrast matrix to test the differences

```{r}
library(dplyr)
NanoSIMSAllDeadNoDay33=filter(NanoSIMSAll,Dead=="no" & Day==33)%>% droplevels() 
head(NanoSIMSAllDeadNoDay33)
str(NanoSIMSAllDeadNoDay33)#to make sure we only keep the live ones



ChangeArea.lm1=lm(Area_mm2_PercentageChange~Culture*Temperature,data=NanoSIMSAllDeadNoDay33)
par(mfrow=c(2,3))
plot(ChangeArea.lm1,which=1:6)
summary(ChangeArea.lm1)


```

```{r}
#contrast matrix
library(contrast)
   a=contrast(ChangeArea.lm1, 
           a=list(Temperature='27',Culture='SS01'), 
           b=list(Temperature='27',Culture='SS08')
   ) 
   str (a) # the matrix is in $ X : num [1, 1:12] as a$X

   b=contrast(ChangeArea.lm1, 
           a=list(Temperature='27',Culture='SS08'), 
           b=list(Temperature='27',Culture='WT10')
   ) 
   str (b) # the matrix is in $ X  : num [1, 1:12]  as b$X
   
   c=contrast(ChangeArea.lm1, 
           a=list(Temperature='27',Culture='SS01'), 
           b=list(Temperature='27',Culture='WT10')
   ) 
   str (c) # the matrix is in the $ X : num [1, 1:12]  as b$X
   
   d=contrast(ChangeArea.lm1, 
           a=list(Temperature='31',Culture='SS01'), 
           b=list(Temperature='31',Culture='SS08')
   ) 
   str (d)
   
   e=contrast(ChangeArea.lm1, 
           a=list(Temperature='31',Culture='SS08'), 
           b=list(Temperature='31',Culture='WT10')
   ) 
   str (e)
   
   f=contrast(ChangeArea.lm1, 
           a=list(Temperature='31',Culture='SS01'), 
           b=list(Temperature='31',Culture='WT10')
   ) 
   str (f)
   
   
   ChangeAreaMatrixTry1=rbind(a$X,b$X,c$X,d$X,e$X,f$X) #create the matrix
   ChangeAreaMatrixTry1

#run the contrast matrix in the model
library(multcomp)
t <- glht(ChangeArea.lm1, linfct = ChangeAreaMatrixTry1)
t
summary(t) 
```
 



#2.2 TO growth

 #2.2.1 Graphs

Look at the data from day 00 
```{r}
str(T00NanoSIMS)
head(T00NanoSIMS)
tail(T00NanoSIMS)
```

Create and Save Summary
```{r}
summaryAreaTO<-summarySE(T00NanoSIMS, measurevar="Area_mm2", groupvars=c("Culture"),na.rm=TRUE,conf.interval=0.95)
summaryAreaTO

library(xlsx)
write.csv(summaryAreaTO,"summaryAreaTO.csv")

summaryAreaTO

```

`
#bar graph 
```{r}
library(ggplot2)
summaryAreaTO$Culture=factor(summaryAreaTO$Culture,levels=c("WT10","SS01","SS08"), labels = c("WT10","SS1","SS8"))#change the order of the factors so that they show in the graph in the desired order
Figure1_AreaTO=ggplot(summaryAreaTO, aes(x=Culture, y=Area_mm2,fill=Culture))+
          scale_fill_manual(values=c("#A4D3CC","#CE9884","#871719"))+        
          geom_bar(stat="identity", position=position_dodge(.9))+
          geom_errorbar(aes(ymin=Area_mm2-se, ymax=Area_mm2+se),position=position_dodge(.9),width=0.3)+
          scale_y_continuous (expression("T"[0]~ "Area (mm"^2~")"))+
          scale_x_discrete('Culture')+        
          theme_bw()
  
Figure1_AreaTO
```

#2.2.2 Stats

     #2.1.2.1 Single Lm and use the contrast matrix to test the differences 
         #find and fit the model
```{r}
head(T00NanoSIMS)
str(T00NanoSIMS)

Area.lm1=lm(Area_mm2~Culture,data=T00NanoSIMS)
par(mfrow=c(2,3))
plot(ChangeArea.lm1,which=1:6) #Meet the asumptions. No wedge shape in the residuals vs fitted and the QQ plot almost follow the straight line
```
#contrast matrix
```{r}
#contrast matrix for the third model
library(contrast)
   a=contrast(Area.lm1, 
           a=list(Culture='SS01'), 
           b=list(Culture='SS08')
   ) 
   str (a) # the matrix is in $ X : num [1, 1:12] as a$X

   b=contrast(Area.lm1, 
           a=list(Culture='SS08'), 
           b=list(Culture='WT10')
   ) 
   str (b) # the matrix is in $ X  : num [1, 1:12]  as b$X
   
   c=contrast(Area.lm1, 
           a=list(Culture='SS01'), 
           b=list(Culture='WT10')
   ) 
   
   AreaMatrixT0=rbind(a$X,b$X,c$X) #create the matrix
   AreaMatrixT0

#run the contrast matrix in the model
library(multcomp)
t <- glht(Area.lm1, linfct = AreaMatrixT0)
t
summary(t) 
```




#3 Survivorship (graph and stats)

```{r}
NanoSIMSPercentSurvivorship<-read.csv("NanoSIMSSurvivorship.csv",header=T,strip.white=TRUE)
head(NanoSIMSPercentSurvivorship)


NanoSIMSPercentSurvivorship$Temperature<-as.factor(NanoSIMSPercentSurvivorship$Temperature)
NanoSIMSPercentSurvivorship$Disk<-as.factor(NanoSIMSPercentSurvivorship$Disk)

head(NanoSIMSPercentSurvivorship)
```


# Summary function
```{r}
summarySE <- function(data=NULL, measurevar, groupvars=NULL, na.rm=FALSE,
                      conf.interval=.95, .drop=TRUE) {
  require(plyr)
  
  
  # New version of length which can handle NA's: if na.rm==T, don't count them
  length2 <- function (x, na.rm=FALSE) {
    if (na.rm) sum(!is.na(x))
    else       length(x)
  }
  
  # This does the summary. For each group's data frame, return a vector with
  # N, mean, and sd
  datac <- ddply(data, groupvars, .drop=.drop,
                 .fun = function(xx, col) {
                   c(N    = length2(xx[[col]], na.rm=na.rm),
                     mean = mean   (xx[[col]], na.rm=na.rm),
                     sd   = sd     (xx[[col]], na.rm=na.rm)
                   )
                 },
                 measurevar
  )
  
  # Rename the "mean" column    
  datac <- rename(datac, c("mean" = measurevar))
  
  datac$se <- datac$sd / sqrt(datac$N)  # Calculate standard error of the mean
  
  # Confidence interval multiplier for standard error
  # Calculate t-statistic for confidence interval: 
  # e.g., if conf.interval is .95, use .975 (above/below), and use df=N-1
  ciMult <- qt(conf.interval/2 + .5, datac$N-1)
  datac$ci <- datac$se * ciMult
  
  return(datac)
}
```

    #3.1.1 Percentage survivorship graph


Create and Save Summary
```{r}
head(NanoSIMSPercentSurvivorship)
summaryNanoPercentSurvivorship<-summarySE(NanoSIMSPercentSurvivorship, measurevar="PercentSurvivorship", groupvars=c("Culture","Temperature"),na.rm=TRUE,conf.interval=0.95)
summaryNanoPercentSurvivorship
```

#bar graph 
```{r}

library(ggplot2)
summaryNanoPercentSurvivorship$Culture=factor(summaryNanoPercentSurvivorship$Culture,levels=c("WT10","SS01","SS08"), labels = c("WT10","SS1","SS8"))#change the order of the factors so that they show in the graph in the desired order

Figure4A_PercentSurvivorship=ggplot(summaryNanoPercentSurvivorship, aes(x=Temperature, y=PercentSurvivorship,fill=Culture))+
          scale_fill_manual(values=c("#A4D3CC","#CE9884","#871719"))+
          geom_bar(stat="identity", position=position_dodge(.9))+
          geom_errorbar(aes(ymin=PercentSurvivorship-se, ymax=PercentSurvivorship+se),position=position_dodge(.9),width=0.3)+
          scale_y_continuous (expression("(T"[33]~") Percentage Survivorship (%)"))+
          scale_x_discrete('Temperature')+
          theme_bw()
Figure4A_PercentSurvivorship
```
    #3.2 Percentage survivorship stats
    
```{r}
head(NanoSIMSPercentSurvivorship)
str(NanoSIMSPercentSurvivorship)

PercentSurvivorship.lm1=lm(PercentSurvivorship~Culture*Temperature,data=NanoSIMSPercentSurvivorship)
par(mfrow=c(2,3))
plot(PercentSurvivorship.lm1,which=1:6)
summary(PercentSurvivorship.lm1)


```

```{r}
#contrast matrix
library(contrast)
   a=contrast(PercentSurvivorship.lm1, 
           a=list(Temperature='27',Culture='SS01'), 
           b=list(Temperature='27',Culture='SS08')
   ) 
   str (a) # the matrix is in $ X : num [1, 1:12] as a$X

   b=contrast(PercentSurvivorship.lm1, 
           a=list(Temperature='27',Culture='SS08'), 
           b=list(Temperature='27',Culture='WT10')
   ) 
   str (b) # the matrix is in $ X  : num [1, 1:12]  as b$X
   
   c=contrast(PercentSurvivorship.lm1, 
           a=list(Temperature='27',Culture='SS01'), 
           b=list(Temperature='27',Culture='WT10')
   ) 
   str (c) # the matrix is in the $ X : num [1, 1:12]  as b$X
   
   d=contrast(PercentSurvivorship.lm1, 
           a=list(Temperature='31',Culture='SS01'), 
           b=list(Temperature='31',Culture='SS08')
   ) 
   str (d)
   
   e=contrast(PercentSurvivorship.lm1, 
           a=list(Temperature='31',Culture='SS08'), 
           b=list(Temperature='31',Culture='WT10')
   ) 
   str (e)
   
   f=contrast(PercentSurvivorship.lm1, 
           a=list(Temperature='31',Culture='SS01'), 
           b=list(Temperature='31',Culture='WT10')
   ) 
   str (f)
   
   
   PercentSurvMatrixTry1=rbind(a$X,b$X,c$X,d$X,e$X,f$X) #create the matrix
   PercentSurvMatrixTry1

#run the contrast matrix in the model
library(multcomp)
t <- glht(PercentSurvivorship.lm1, linfct = PercentSurvMatrixTry1)
t
summary(t) 
```    
    


#4 RESPIRATION

Filter data to keep just T00 and T33
```{r}
library(dplyr)
head(NanoSIMSAll)

RespNanoSIMS=filter(NanoSIMSAll,DayAsFactor=='0' | DayAsFactor=='33')%>% droplevels() 
str(RespNanoSIMS)

RespNanoSIMST00=filter(RespNanoSIMS,DayAsFactor=='0')%>% droplevels()
str(RespNanoSIMST00)

RespNanoSIMST33=filter(RespNanoSIMS,DayAsFactor=='33')%>% droplevels()
str(RespNanoSIMST00)

RespNanoSS01=filter(RespNanoSIMS,Culture=='SS01')%>% droplevels()
str(RespNanoSS01)

RespNanoSS08=filter(RespNanoSIMS,Culture=='SS08')%>% droplevels()
str(RespNanoSS08)
```


Create and Save Summary
```{r}
summaryRespPerMM2<-summarySE(RespNanoSIMS, measurevar="RespirationPerMM2", groupvars=c("DayAsFactor","Treatment","Culture","Temperature"),na.rm=TRUE,conf.interval=0.95)
summaryRespPerMM2 #this will produce NaN because we didn't do one of the treatments WT10@27C
```
#4.1 bar graph 

```{r}
library(ggplot2)
summaryRespPerMM2$Culture=factor(summaryRespPerMM2$Culture,levels=c("WT10","SS01","SS08"), labels = c("WT10","SS1","SS8"))#change the order of the factors so that they show in the graph in the desired order

Figure3_RespirationPerMM2=ggplot(summaryRespPerMM2, aes(x=Temperature, y=RespirationPerMM2,fill=Culture))+
          scale_fill_manual(values=c("#A4D3CC","#CE9884","#871719"))+
          geom_bar(stat="identity", position=position_dodge(.9))+
          facet_grid(.~DayAsFactor,scale="free")+
          geom_errorbar(aes(ymin=RespirationPerMM2-se, ymax=RespirationPerMM2+se), position=position_dodge(.9),width=0.3)+
          scale_y_continuous (expression("O"[2]~"(mg h"^-1~"mm"^-2~")")) +
          scale_x_discrete('Temperature')+
          theme_bw()

Figure3_RespirationPerMM2
```
#4.2 Stats
Look at the data of day 00 
```{r}
str(T00NanoSIMS)
head(T00NanoSIMS)
tail(T00NanoSIMS)
```
```{r}
library(dplyr)
T00NanoSIMS27=filter(T00NanoSIMS,Temperature=='27')%>% droplevels()
T00NanoSIMS31=filter(T00NanoSIMS,Temperature=='31')%>% droplevels()
T00NanoSS1SIMS=filter(T00NanoSIMS,Culture=='SS01')%>% droplevels()
T00NanoSS8SIMS=filter(T00NanoSIMS,Culture=='SS08')%>% droplevels()

str(T00NanoSIMS27)
str(T00NanoSIMS31)
str(T00NanoSS1SIMS)
str(T00NanoSS8SIMS)
```


Linear model T00 and 27C
```{r}
Resp27CT00.lm1=lm(RespirationPerMM2~Culture,data=T00NanoSIMS27)
par(mfrow=c(2,3))
plot(Resp27CT00.lm1,which=1:6)
summary(Resp27CT00.lm1)
```
Linear model T00 and 31C
```{r}
Resp31CT00.lm1=lm(RespirationPerMM2~Culture,data=T00NanoSIMS31)
par(mfrow=c(2,3))
plot(Resp31CT00.lm1,which=1:6)
summary(Resp31CT00.lm1)
```
#contrast matrix

   
```{r}
library(contrast)
   a=contrast(Resp31CT00.lm1, 
           a=list(Culture='SS01'), 
           b=list(Culture='SS08')
   ) 
   str (a) # the matrix is in the $ X : num [1, 1:12]  as b$X
   b=contrast(Resp31CT00.lm1, 
           a=list(Culture='SS01'), 
           b=list(Culture='WT10')
   ) 
   str (b) # the matrix is in the $ X : num [1, 1:12]  as b$X
   c=contrast(Resp31CT00.lm1, 
           a=list(Culture='SS08'), 
           b=list(Culture='WT10')
   ) 
   str (c)
   
   Resp31CT00MatrixTry1=rbind(a$X,b$X,c$X) #create the matrix
   Resp31CT00MatrixTry1

#run the contrast matrix in the model
library(multcomp)
rt31T00 <- glht(Resp31CT00.lm1, linfct = Resp31CT00MatrixTry1)
rt31T00
summary(rt31T00) 
```

Linear model T00 and SS1
```{r}
RespSS1T00.lm1=lm(RespirationPerMM2~Temperature,data=T00NanoSS1SIMS)
par(mfrow=c(2,3))
plot(RespSS1T00.lm1,which=1:6)
summary(RespSS1T00.lm1)
```


Linear model T00 and SS8
```{r}
RespSS8T00.lm1=lm(RespirationPerMM2~Temperature,data=T00NanoSS8SIMS)
par(mfrow=c(2,3))
plot(RespSS8T00.lm1,which=1:6)
summary(RespSS8T00.lm1)
```


Linear model
```{r}
RespT33.lm1=lm(RespirationPerMM2~Culture*Temperature,data=T33NanoSIMS)
par(mfrow=c(2,3))
plot(RespT33.lm1,which=1:6)
summary(RespT33.lm1)
```


```{r}
#contrast matrix
library(contrast)
   a=contrast(RespT33.lm1, 
           a=list(Temperature='27',Culture='SS01'), 
           b=list(Temperature='27',Culture='SS08')
   ) 
   str (a) # the matrix is in $ X : num [1, 1:12] as a$X

   b=contrast(RespT33.lm1, 
           a=list(Temperature='27',Culture='SS01'), 
           b=list(Temperature='27',Culture='WT10')
   ) 
   str (b) # the matrix is in $ X  : num [1, 1:12]  as b$X
   
   c=contrast(RespT33.lm1, 
           a=list(Temperature='27',Culture='SS08'), 
           b=list(Temperature='27',Culture='WT10')
   ) 
   str (c) # the matrix is in the $ X : num [1, 1:12]  as b$X
   
   d=contrast(RespT33.lm1, 
           a=list(Temperature='27',Culture='SS01'), 
           b=list(Temperature='31',Culture='SS01')
   ) 
   str (d)
   
   e=contrast(RespT33.lm1, 
           a=list(Temperature='27',Culture='SS08'), 
           b=list(Temperature='31',Culture='SS08')
   ) 
   str (e)
   
   f=contrast(RespT33.lm1, 
           a=list(Temperature='27',Culture='WT10'), 
           b=list(Temperature='31',Culture='WT10')
   ) 
   str (f)
   g=contrast(RespT33.lm1, 
           a=list(Temperature='31',Culture='SS01'), 
           b=list(Temperature='31',Culture='SS08')
   ) 
   str (g) # the matrix is in $ X : num [1, 1:12] as a$X

   h=contrast(RespT33.lm1, 
           a=list(Temperature='31',Culture='SS01'), 
           b=list(Temperature='31',Culture='WT10')
   ) 
   str (h) # the matrix is in $ X  : num [1, 1:12]  as b$X
   
   i=contrast(RespT33.lm1, 
           a=list(Temperature='31',Culture='SS08'), 
           b=list(Temperature='31',Culture='WT10')
   ) 
   str (i) # the matrix is in the $ X : num [1, 1:12]  as b$X
 
   
   RespT33MatrixTry1=rbind(a$X,b$X,c$X,d$X,e$X,f$X,g$X,h$X,i$X) #create the matrix
   RespT33MatrixTry1

#run the contrast matrix in the model
library(multcomp)
rt33 <- glht(RespT33.lm1, linfct = RespT33MatrixTry1)
rt33
summary(rt33) 
```    


Linear model 27C
```{r}
head(RespNanoSIMS)
Resp.lm1=lm(RespirationPerMM2~Culture*DayAsFactor*Temperature,data=RespNanoSIMS)
par(mfrow=c(2,3))
plot(Resp.lm1,which=1:6)
summary(Resp.lm1)
```

```{r}
#contrast matrix
str(RespNanoSIMS$DayAsFactor)
str(RespNanoSIMS)
library(contrast)
   a=contrast(Resp.lm1, 
           a=list(DayAsFactor="0",Temperature='27',Culture='SS01'), 
           b=list(DayAsFactor="33",Temperature='27',Culture='SS01')
   ) 
   str (a) # the matrix is in $ X : num [1, 1:12] as a$X

   b=contrast(Resp.lm1, 
           a=list(DayAsFactor="0",Temperature='27',Culture='SS08'), 
           b=list(DayAsFactor="33",Temperature='27',Culture='SS08')
   ) 
   str (b) # the matrix is in $ X  : num [1, 1:12]  as b$X
   
   
   
   Resp27CMatrixTry1=rbind(a$X,b$X) #create the matrix
   Resp27CMatrixTry1

#run the contrast matrix in the model
library(multcomp)
rt27C <- glht(Resp.lm1, linfct = Resp27CMatrixTry1)
rt27C
summary(rt27C) 
```    

#5 Cell densities 
    #5.1 Bar graph Cell densities per mm2
Create and Save Summary
```{r}
head(T0033NanoSIMS)
summaryCellPerMM2<-summarySE(T0033NanoSIMS, measurevar="CellsPerMM2", groupvars=c("DayAsFactor","Culture","Temperature","Treatment"),na.rm=TRUE,conf.interval=0.95)
summaryCellPerMM2
```



#bar graph 
```{r}
library(ggplot2)
summaryCellPerMM2$Culture=factor(summaryCellPerMM2$Culture,levels=c("WT10","SS01","SS08"), labels = c("WT10","SS1","SS8"))#change the order of the factors so that they show in the graph in the desired order
Figure2A_CellPerMM2Graph=ggplot(summaryCellPerMM2, aes(x=Temperature, y=CellsPerMM2,fill=Culture))+
          scale_fill_manual(values=c("#A4D3CC","#CE9884","#871719"))+        
          geom_bar(stat="identity", position=position_dodge(.9))+
          facet_grid(.~DayAsFactor,scale="free")+
          geom_errorbar(aes(ymin=CellsPerMM2-se, ymax=CellsPerMM2+se), position=position_dodge(.9),width=0.3)+
          scale_y_continuous (expression("Cells mm"^-2))+
          scale_x_discrete('Temperature')+
          theme_bw()

Figure2A_CellPerMM2Graph
```

        #5.1.1 Linear model T00

```{r}
head(T00NanoSIMS)
str(T00NanoSIMS)

T00CellPerMM2.lm1=lm(CellsPerMM2~Culture*Temperature,data=T00NanoSIMS)
par(mfrow=c(2,3))
plot(T00CellPerMM2.lm1,which=1:6)
summary(T00CellPerMM2.lm1)
```

```{r}
#contrast matrix
library(contrast)
   a=contrast(T00CellPerMM2.lm1, 
           a=list(Temperature='27',Culture='SS01'), 
           b=list(Temperature='27',Culture='SS08')
   ) 
   str (a) # the matrix is in $ X : num [1, 1:12] as a$X

   b=contrast(T00CellPerMM2.lm1, 
           a=list(Temperature='27',Culture='SS01'), 
           b=list(Temperature='27',Culture='WT10')
   ) 
   str (b) # the matrix is in $ X  : num [1, 1:12]  as b$X
   
   c=contrast(T00CellPerMM2.lm1, 
           a=list(Temperature='27',Culture='SS08'), 
           b=list(Temperature='27',Culture='WT10')
   ) 
   str (c) # the matrix is in the $ X : num [1, 1:12]  as b$X
   
   d=contrast(T00CellPerMM2.lm1, 
           a=list(Temperature='27',Culture='SS01'), 
           b=list(Temperature='31',Culture='SS01')
   ) 
   str (d)
   
   e=contrast(T00CellPerMM2.lm1, 
           a=list(Temperature='27',Culture='SS08'), 
           b=list(Temperature='31',Culture='SS08')
   ) 
   str (e)
   
   f=contrast(T00CellPerMM2.lm1, 
           a=list(Temperature='27',Culture='WT10'), 
           b=list(Temperature='31',Culture='WT10')
   ) 
   str (f)
   g=contrast(T00CellPerMM2.lm1, 
           a=list(Temperature='31',Culture='SS01'), 
           b=list(Temperature='31',Culture='SS08')
   ) 
   str (g) # the matrix is in $ X : num [1, 1:12] as a$X

   h=contrast(T00CellPerMM2.lm1, 
           a=list(Temperature='31',Culture='SS01'), 
           b=list(Temperature='31',Culture='WT10')
   ) 
   str (h) # the matrix is in $ X  : num [1, 1:12]  as b$X
   
   i=contrast(T00CellPerMM2.lm1, 
           a=list(Temperature='31',Culture='SS08'), 
           b=list(Temperature='31',Culture='WT10')
   ) 
   str (i) # the matrix is in the $ X : num [1, 1:12]  as b$X
 
   
  T00CellPerMM2Try1=rbind(a$X,b$X,c$X,d$X,e$X,f$X,g$X,h$X,i$X) #create the matrix
  T00CellPerMM2Try1

#run the contrast matrix in the model
library(multcomp)
cellpermm2t00<- glht(T00CellPerMM2.lm1, linfct = T00CellPerMM2Try1)
cellpermm2t00
summary(cellpermm2t00) 
```

        #5.1.2 Linear model T33

```{r}
head(T33NanoSIMS)
str(T33NanoSIMS)

T33CellPerMM2.lm1=lm(CellsPerMM2~Culture*Temperature,data=T33NanoSIMS)
par(mfrow=c(2,3))
plot(T33CellPerMM2.lm1,which=1:6)
summary(T33CellPerMM2.lm1)
```

```{r}
#contrast matrix
library(contrast)
   a=contrast(T33CellPerMM2.lm1, 
           a=list(Temperature='27',Culture='SS01'), 
           b=list(Temperature='27',Culture='SS08')
   ) 
   str (a) # the matrix is in $ X : num [1, 1:12] as a$X

   b=contrast(T33CellPerMM2.lm1, 
           a=list(Temperature='27',Culture='SS01'), 
           b=list(Temperature='27',Culture='WT10')
   ) 
   str (b) # the matrix is in $ X  : num [1, 1:12]  as b$X
   
   c=contrast(T33CellPerMM2.lm1, 
           a=list(Temperature='27',Culture='SS08'), 
           b=list(Temperature='27',Culture='WT10')
   ) 
   str (c) # the matrix is in the $ X : num [1, 1:12]  as b$X
   
   d=contrast(T33CellPerMM2.lm1, 
           a=list(Temperature='27',Culture='SS01'), 
           b=list(Temperature='31',Culture='SS01')
   ) 
   str (d)
   
   e=contrast(T33CellPerMM2.lm1, 
           a=list(Temperature='27',Culture='SS08'), 
           b=list(Temperature='31',Culture='SS08')
   ) 
   str (e)
   
   f=contrast(T33CellPerMM2.lm1, 
           a=list(Temperature='27',Culture='WT10'), 
           b=list(Temperature='31',Culture='WT10')
   ) 
   str (f)
   g=contrast(T33CellPerMM2.lm1, 
           a=list(Temperature='31',Culture='SS01'), 
           b=list(Temperature='31',Culture='SS08')
   ) 
   str (g) # the matrix is in $ X : num [1, 1:12] as a$X

   h=contrast(T33CellPerMM2.lm1, 
           a=list(Temperature='31',Culture='SS01'), 
           b=list(Temperature='31',Culture='WT10')
   ) 
   str (h) # the matrix is in $ X  : num [1, 1:12]  as b$X
   
   i=contrast(T33CellPerMM2.lm1, 
           a=list(Temperature='31',Culture='SS08'), 
           b=list(Temperature='31',Culture='WT10')
   ) 
   str (i) # the matrix is in the $ X : num [1, 1:12]  as b$X
 
   
  T33CellPerMM2Try1=rbind(a$X,b$X,c$X,d$X,e$X,f$X,g$X,h$X,i$X) #create the matrix
  T33CellPerMM2Try1

#run the contrast matrix in the model
library(multcomp)
cellpermm2t33<- glht(T33CellPerMM2.lm1, linfct = T33CellPerMM2Try1)
cellpermm2t33
summary(cellpermm2t33) 
```


   #5.2 Bar graph Propor Change in Cell densities per mm2
Create and Save Summary
```{r}
head(T33NanoSIMS)
summaryCellPerMM2PropChange<-summarySE(T33NanoSIMS, measurevar="CellDensityPerMM2PercentChange", groupvars=c("Culture","Temperature","Treatment"),na.rm=TRUE,conf.interval=0.95)
summaryCellPerMM2PropChange
```

```{r}

summaryCellPerMM2PropChange$Culture=factor(summaryCellPerMM2PropChange$Culture,levels=c("WT10","SS01","SS08"), labels = c("WT10","SS1","SS8"))#change the order of the factors so that they show in the graph in the desired order

Figure2B1_CellPerMM2PropChange=ggplot(summaryCellPerMM2PropChange, aes(x=Temperature, y=CellDensityPerMM2PercentChange,fill=Culture))+
          scale_fill_manual(values=c("#A4D3CC","#CE9884","#871719"))+
          geom_bar(stat="identity", position=position_dodge(.9))+
          geom_errorbar(aes(ymin=CellDensityPerMM2PercentChange-se, ymax=CellDensityPerMM2PercentChange+se),position=position_dodge(.9),width=0.3)+
          scale_y_continuous (expression("(T"[33]~") Percentage of Change of "~"cells mm"^-2~"(%)"))+    
          scale_x_discrete('Temperature')+
          theme_bw()
Figure2B1_CellPerMM2PropChange
```

      #5.2.1 Linear model
  Linear model
```{r}
PropChangeCellsMM2.lm1=lm(CellDensityPerMM2PercentChange~Culture*Temperature,data=T33NanoSIMS)
par(mfrow=c(2,3))
plot(PropChangeCellsMM2.lm1,which=1:6)
summary(PropChangeCellsMM2.lm1)
```

```{r}
#contrast matrix
library(contrast)
   a=contrast(PropChangeCellsMM2.lm1, 
           a=list(Temperature='27',Culture='SS01'), 
           b=list(Temperature='27',Culture='SS08')
   ) 
   str (a) # the matrix is in $ X : num [1, 1:12] as a$X

   b=contrast(PropChangeCellsMM2.lm1, 
           a=list(Temperature='27',Culture='SS01'), 
           b=list(Temperature='27',Culture='WT10')
   ) 
   str (b) # the matrix is in $ X  : num [1, 1:12]  as b$X
   
   c=contrast(PropChangeCellsMM2.lm1, 
           a=list(Temperature='27',Culture='SS08'), 
           b=list(Temperature='27',Culture='WT10')
   ) 
   str (c) # the matrix is in the $ X : num [1, 1:12]  as b$X
   
   d=contrast(PropChangeCellsMM2.lm1, 
           a=list(Temperature='27',Culture='SS01'), 
           b=list(Temperature='31',Culture='SS01')
   ) 
   str (d)
   
   e=contrast(PropChangeCellsMM2.lm1, 
           a=list(Temperature='27',Culture='SS08'), 
           b=list(Temperature='31',Culture='SS08')
   ) 
   str (e)
   
   f=contrast(PropChangeCellsMM2.lm1, 
           a=list(Temperature='27',Culture='WT10'), 
           b=list(Temperature='31',Culture='WT10')
   ) 
   str (f)
   g=contrast(PropChangeCellsMM2.lm1, 
           a=list(Temperature='31',Culture='SS01'), 
           b=list(Temperature='31',Culture='SS08')
   ) 
   str (g) # the matrix is in $ X : num [1, 1:12] as a$X

   h=contrast(PropChangeCellsMM2.lm1, 
           a=list(Temperature='31',Culture='SS01'), 
           b=list(Temperature='31',Culture='WT10')
   ) 
   str (h) # the matrix is in $ X  : num [1, 1:12]  as b$X
   
   i=contrast(PropChangeCellsMM2.lm1, 
           a=list(Temperature='31',Culture='SS08'), 
           b=list(Temperature='31',Culture='WT10')
   ) 
   str (i) # the matrix is in the $ X : num [1, 1:12]  as b$X
 
   
   PropChangeCellsMM2T33MatrixTry1=rbind(a$X,b$X,c$X,d$X,e$X,f$X,g$X,h$X,i$X) #create the matrix
   PropChangeCellsMM2T33MatrixTry1

#run the contrast matrix in the model
library(multcomp)
pchanget33 <- glht(PropChangeCellsMM2.lm1, linfct = PropChangeCellsMM2T33MatrixTry1)
pchanget33
summary(pchanget33) 
```


    #5.3 Propor Change in Cell densities per mm2 per time point within culture and temp change 
        
        
        
 summary       
```{r}       
head(T0033NanoSIMS)  
summaryCellPerMM2PropChangePerTimePoint<-summarySE(T0033NanoSIMS, measurevar="CellDensityPerMM2PercentChangePerTimePointAndCulture", groupvars=c("DayAsFactor","Culture"),na.rm=TRUE,conf.interval=0.95)
summaryCellPerMM2PropChangePerTimePoint
```     
        
  #5.3.1 Bar graph       
        
```{r}
head(NanoSIMSAll)
summaryCellPerMM2PropChangePerTimePoint$Culture=factor(summaryCellPerMM2PropChangePerTimePoint$Culture,levels=c("WT10","SS01","SS08"), labels = c("WT10","SS1","SS8"))#change the order of the factors so that they show in the graph in the desired order

Figure2B2_CellPerMM2PropChangePerTimePoint=ggplot(summaryCellPerMM2PropChangePerTimePoint, 
                                                  aes(x=DayAsFactor, 
                                                      y=CellDensityPerMM2PercentChangePerTimePointAndCulture,
                                                      fill=Culture))+
          scale_fill_manual(values=c("#A4D3CC","#CE9884","#871719"))+
          geom_bar(stat="identity", position=position_dodge(.9))+
          geom_errorbar(aes(ymin=CellDensityPerMM2PercentChangePerTimePointAndCulture-se,
                            ymax=CellDensityPerMM2PercentChangePerTimePointAndCulture+se),
                            position=position_dodge(.9),width=0.3)+
          scale_y_continuous (expression("Percentage of Change in "~"cells mm"^-2~"After Temperature Increase(%)"))+    
          scale_x_discrete('Day')+
          theme_bw()
Figure2B2_CellPerMM2PropChangePerTimePoint
```

      #5.3.2 Linear model
  Linear model
```{r}
PropChangeInCellsMM2PerChangeInTempWithinCulture.lm1=lm(CellDensityPerMM2PercentChangePerTimePointAndCulture~Culture*DayAsFactor,data=T0033NanoSIMS)
par(mfrow=c(2,3))
plot(PropChangeInCellsMM2PerChangeInTempWithinCulture.lm1,which=1:6)
summary(PropChangeInCellsMM2PerChangeInTempWithinCulture.lm1)
```

```{r}
#contrast matrix
library(contrast)
   a=contrast(PropChangeInCellsMM2PerChangeInTempWithinCulture.lm1, 
           a=list(DayAsFactor='0',Culture='WT10'), 
           b=list(DayAsFactor='0',Culture='SS01')
   ) 
   str (a) # the matrix is in $ X : num [1, 1:12] as a$X

   b=contrast(PropChangeInCellsMM2PerChangeInTempWithinCulture.lm1, 
           a=list(DayAsFactor='0',Culture='WT10'), 
           b=list(DayAsFactor='0',Culture='SS08')
   ) 
   str (b) # the matrix is in $ X  : num [1, 1:12]  as b$X
   
   c=contrast(PropChangeInCellsMM2PerChangeInTempWithinCulture.lm1, 
           a=list(DayAsFactor='0',Culture='SS01'), 
           b=list(DayAsFactor='0',Culture='SS08')
   ) 
   str (c) # the matrix is in the $ X : num [1, 1:12]  as b$X
   
   d=contrast(PropChangeInCellsMM2PerChangeInTempWithinCulture.lm1, 
           a=list(DayAsFactor='33',Culture='WT10'), 
           b=list(DayAsFactor='33',Culture='SS01')
   ) 
   str (d)
   
   e=contrast(PropChangeInCellsMM2PerChangeInTempWithinCulture.lm1, 
           a=list(DayAsFactor='33',Culture='WT10'), 
           b=list(DayAsFactor='33',Culture='SS08')
   ) 
   str (e)
   
   f=contrast(PropChangeInCellsMM2PerChangeInTempWithinCulture.lm1, 
           a=list(DayAsFactor='33',Culture='SS01'), 
           b=list(DayAsFactor='33',Culture='SS08')
   ) 
   str (f)
   
   PropChangeCellsMM2InTempWithinCultureMatrixTry1=rbind(a$X,b$X,c$X,d$X,e$X,f$X) #create the matrix
   PropChangeCellsMM2InTempWithinCultureMatrixTry1

#run the contrast matrix in the model
library(multcomp)
pchanget0And33 <- glht(PropChangeInCellsMM2PerChangeInTempWithinCulture.lm1, linfct = PropChangeCellsMM2InTempWithinCultureMatrixTry1)
pchanget0And33
summary(pchanget0And33) 
```










